Large-eddy simulations of the ice-shelf oceanic boundary layer

### 2021-01-18 A01_ice_surface_fluxes.tex
Text update 20210118

Momentum flux

    Components of surface stress $\tau_i$
    \begin{equation*}
    \tau_i = \rho \overline{u_i''w''}
    \end{equation*}
    for i = 1,2.

    Friction velocity $u_*$
    \begin{equation*}
    u_*^2=|\tau_0|^{1/2}
    \end{equation*}
    % \begin{equation*}
    % u_*^2=(\overline{u''w''}^2 + \overline{v''w''}^2)^{1/2}
    % \end{equation*}

    Turbulence closure
    \begin{equation*}
    \overline{u_i''w''} = k_m \frac{\partial u_i}{\partial z}
    \end{equation*}

    There is empirical support for a linear increase in eddy diffusivity from the wall
    \begin{equation*}
    u_* = \frac{k z}{\Psi_m(\zeta) } \frac{\partial u}{\partial z}
    \end{equation*}
    where $\zeta = z/L_O$

    We integrate using this relationship (or $\Psi = 1$ to get $u_*$
    \begin{equation*}
    \Psi_m(\zeta) = 1 + \beta_m \zeta
    \end{equation*}
    where $\beta_m = 4.8$ (Wyngaard 2010; Zhou et al. 2017)

    We integrate using this relationship to get $u_i''w''$
    \begin{equation*}
    \beta_m = (\frac{1}{R_c} + \frac{f L_O}{u_* \chi_N})(1-\eta_*)
    \end{equation*}
    (McPhee 1981)

    % Integrating for $u(z)$ (this is never needed because all we need is stress
    % \begin{equation*}
    % u = \frac{u_*}{k} ln(frac{z}{z_0} + \frac{\beta_m}{k}\zeta + C_m
    %\end{equation*}
    % \begin{equation*}
    % u = \frac{u_*}{k} ln(frac{z}{z_0} = c_d(z)^{\frac{-1}{2}}u_*
    % \end{equation*}
    % The friction velocity is defined following "law of the wall"
    % \begin{equation}
    %     u_* = \kappa u_m / log(z_m/z_0)
    % \end{equation}

    \begin{equation*}
    \overline{u_i''w''}(z_1) = u_* (\phi_i(\textbf{u(z_1)}))
    \end{equation*}

    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.

    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic). We denote this depth $z_m$.

    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
    \begin{equation}
        \zeta = \frac{z}{\eta_* u_*/f}
    \end{equation}

    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
    \begin{equation}
        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
    \end{equation}
    where $L_O$ is the Monin-Obukhov length
    \begin{equation}
        L_O = \rho \frac{u_*^3}{\kappa F_B}
    \end{equation}

    \begin{equation}
	F_B = g(\beta w'S' - \alpha w'\theta')
	\end{equation}

    \begin{equation}
        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
    \end{equation}
    \begin{equation}
        \phi_1 = (u_1* RE(\tau) + u_2* IM(\tau))
    \end{equation}
    \begin{equation}
        \phi_2 = (u_2* RE(\tau) + u_1* IM(\tau))
    \end{equation}

    \begin{equation}
        u''w'' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
    \end{equation}
    \begin{equation}
        v''w'' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
    \end{equation}

>>>>

The turbulence closure scheme is Anisotropic Minimum Dissipation (Rozema) employing the extension to scalars introduced by Abkar and Moin. Our implementation shows similar qualitative behavior to the stable atmospheric boundary layer published in XX; some inter-model variability is expected due to different numerics.

Momentum and scalar fluxes at the top of the domain are parameterized assuming law of the wall and a linear stability function in which depth is scaled by the Monin-Obukhov length, following Vreugdenhil and Taylor (2019). Details can be found in Appendix XX. Scalar fluxes at the top of the domain take the ``virtual" freshwater flux form \cite{XX}. The solution for ice-shelf melting at the interface follows the standard procedure of solving three equations -- local heat conservation, local salt conservation, and the interface temperature set to the freezing point -- for three unknowns, the temperature and salinity at the ice-ocean interface, and the melt rate. This is the so-called three-equation parameterization. For the freezing temperature equation we use the polynomial function from \cite{jackett_2006}. We also assume that the conductive heat flux into ice is zero, as it is typically no more than 10\% of the latent heat used for melting.

### 2021-01-18 main.tex
Text update 20210118

\documentclass[draft]{styles/agujournal2019}
\usepackage{url} 
\usepackage{lineno}
\linenumbers
\draftfalse
\journalname{JGR: Oceans}

\begin{document}
\input{agu_begindoc.tex}

\section{Introduction}

\paragraph{}% from CK application
Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.  Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise.  These critical processes are not captured by even the most advanced Earth System Models (ESMs), such as the DOE’s Energy Exascale Earth System Model (E3SM), of which LANL is a major developer. Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas. Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete. A fundamental understanding of turbulent flow in this unusual regime is lacking, despite widespread adoption and application of existing parameterizations by the international ocean, ice sheet, and ESM communities.

% from postdoc proposal
The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet. The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice. In turn, the Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base; accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL. One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution. Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL. This model deficiency likely biases turbulent fluxes through the IOBL and sub-ice-shelf ocean circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting. A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.

I propose to develop a new parameterization of ice-shelf melting by modeling turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES). Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity. During the first year of the project, I will simulate the IOBL using the MIT General Circulation Model (MITgcm) in a LES ocean configuration. An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface. I will vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates when the modeled IOBL has equilibrated.  During the second year of the project, I will implement the resulting parameterization in the Model for Prediction Across Scales Ocean (MPAS-O), the ocean component of DOE’s new Energy Exascale Earth System Model (E3SM). Using MPAS-O in idealized configurations, I will investigate the parameterization’s impact on sub-ice-shelf ocean circulation and the distribution of ice-shelf melting as compared with previous parameterizations. I will focus on the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse. Resources for this work include MPAS-O, developed at LANL, and existing allocations at a number of DOE HPC facilities (including LANL).

The proposed work, characterizing turbulence in the presence of a buoyancy flux and sloping boundary, addresses a fundamental problem in fluid dynamics. The work also has direct societal relevance because ice-ocean interactions are believed to be a major control on future sea level rise. This new parameterization for ice-shelf melting will support an ongoing effort at LANL and other national labs to accurately couple ice sheet and ocean models and will be exportable from MPAS-O to other models. Thus, in addition to significantly improving simulations of ocean circulation, Antarctic ice loss, and sea level rise in E3SM, it could provide similar advances to other Earth system modeling efforts.

@@

	%\paragraph{The PALM model}
    The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany). It has been applied to the simulation of atmospheric and ocean boundary layers. However, it has never been used specifically to treat a sub-ice-shelf ocean boundary layer. For this application, the key model development was the implementation of dynamic melting fluxes.

@@

	The terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow (imposing incompressibility), and sub-grid scale momentum fluxes.

	\paragraph{Sloping surface}
	We represent a sloping ice base by rotating the gravity and Coriolis vectors while keeping the domain a rectangular prism. The ice base always slopes in the x-dimension of our domain. 
	%In PALM v0 the buoyancy terms were based only on temperature rather than density. 
	Thus, 
	\begin{equation} \label{eq:g}
    	\textbf{g} = g [sin \alpha,0,cos \alpha]
    \end{equation}
	\begin{equation} \label{eq:f}
        \textbf{f} = 2 \Omega [sin \phi sin \alpha,cos \phi,sin \phi cos \alpha]
	\end{equation}

	The buoyancy term combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density. The along-slope pressure gradient is set by the ambient density of the water column $\rho_a$. This ambient density is determined using the far-field temperature and salinity values and the initial vertical hydrostatic pressure profile in the middle of the domain. Thus, we assume that the evolution of density in the boundary layer does not significantly affect ice-shelf slope. We also assume that 
	\begin{equation}
	    \rho(T(x,z),S(x,z),p(x,z)) - \rho_a(T_a,S_a,p(x,z)) \approx 
	    \rho(T(x,z),S(x,z),p(x_{mid},z) - \rho_a(T_a,S_a,p(x_{mid},z))
	\end{equation}
	In other words, we assume that density differences between ambient and simulated conditions does not significantly change as a function of along-slope pressure changes. These density differences are verified to be within XX $kg/m^3$ for these simulations. This simplification has the advantage of avoiding pressure discontinuities across periodic boundary conditions.

	\paragraph{Surface drag}
	The last term in Equation \ref{eq:uprog} represents the loss of momentum due to drag between the ice surface and the flow, where $\tau$ is the shear stress. We discuss the parameterization of $\tau$ in XX.

@@

	%Turbulence closure by the gradient mean approximation
	%\begin{equation} \label{eq:momdiff}
	%\overline{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
    %\end{equation}

	%\begin{equation} \label{eq:ptdiff}
	%\overline{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
	%\end{equation}

	%\begin{equation} \label{eq:e}
	%e = \frac{1}{2}\overline{u'_i u'_i}
	%\end{equation}

    Prognostic equation for Resolved TKE
	\begin{equation} \label{eq:eprog}
	\frac{\partial e^*}{\partial t} = 
	-u_j \frac{\partial e^*}{\partial x_j} 
	- (\overline{u^*_i u^*_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u^*_i \rho^*}
	\end{equation}

	The turbulence closure scheme is XX. We refer the readers to XX for the details.

	Large-scale horizontal pressure gradients are used to drive mean flow and mean shear.

	%\paragraph{Initial and boundary conditions}
	Boundary conditions for velocity, temperature and salinity are cyclic at the side boundaries, dirichlet at the bottom boundary, and von Neumann at the top boundary. 
	The bottom third of the domain is a sponge layer within which velocity, temperature, and salinity are relaxed toward their values at the bottom of the domain. The temperature and salinity at the bottom of the domain are chosen to represent typical sub-ice-shelf water masses. XX. The sponge layer results in no vertical fluxes of heat, salt, or momentum across the bottom boundary.

@@

\subsection{Tables}
\input{table1.tex}

>>>>

\documentclass[draft]{styles/agujournal2019}
\usepackage{url} 
\usepackage{lineno}

\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
\myexternaldocument{A_suppl_fig}

\linenumbers
\draftfalse
\journalname{JGR: Oceans}

\begin{document}
%\input{agu_begindoc.tex}
\title{Large-eddy simulations of the ice-shelf oceanic boundary layer}

\correspondingauthor{Carolyn Begeman}{cbegeman@lanl.gov}
\authors{Carolyn Branecky Begeman\affil{1},Xylar Asay-Davis\affil{1}, and Luke Van Roekel\affil{1}}

\affiliation{1}{Los Alamos National Laboratory, Los Alamos, New Mexico, USA}

\begin{keypoints}
\item 
\item 
\item 
\end{keypoints}

\begin{abstract}
Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.  Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise. Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas. Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete. A fundamental understanding of turbulent flow in this unusual regime is lacking, despite widespread adoption and application of existing parameterizations by the international ocean, ice sheet, and ESM communities.

\textbf{Plain language summary}\\

\end{abstract}
\newpage
\section{Introduction}

\paragraph{}
The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet. The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice. The Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base. Thus, accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL. This representation is also critical for evaluating the sensitivity of the coupled land-ice ocean system.

\paragraph{}
The sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.

\paragraph{}
One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution. Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL. This model deficiency likely biases turbulent fluxes through the IOBL and sub-ice-shelf ocean circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting. A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.

\paragraph{}
In this study, we model turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES). Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity. An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface. We vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates.

\paragraph{}
Characterizing turbulence in the presence of a buoyancy flux and sloping boundary is a fundamental problem in fluid dynamics.

@@

\paragraph{The PALM model}
The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany). It has been applied to the simulation of atmospheric and ocean boundary layers. However, it has never been used specifically to treat a sub-ice-shelf ocean boundary layer. For this application, the key model development was the implementation of dynamic melting fluxes.

\subsection{Governing equations}

@@

The terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow (imposing incompressibility), and sub-grid scale momentum fluxes. 
% Prognostic equation for Resolved TKE
% \begin{equation} \label{eq:eprog}
% \frac{\partial e^*}{\partial t} = 
% -u_j \frac{\partial e^*}{\partial x_j} 
% - (\overline{u^*_i u^*_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u^*_i \rho^*}
% \end{equation}

%\paragraph{}% Sloping surface
We represent a sloping ice base by rotating the gravity and Coriolis vectors while keeping the domain a rectangular prism. 
%In PALM v0 the buoyancy terms were based only on temperature rather than density. 
Thus, 
\begin{equation} \label{eq:g}
	%\textbf{g} = g [sin \alpha,0,cos \alpha]
	\textbf{g} = g [sin \alpha sin \beta,cos \beta,cos \alpha]
\end{equation}
\begin{equation} \label{eq:f}
    \textbf{f} = 2 \Omega [sin \phi sin \alpha,cos \phi,sin \phi cos \alpha]
\end{equation}
$\beta$ is the angle the slope direction makes with north.
$\alpha$ is the slope angle from horizontal
$\phi$ is the latitude.
The ice base always slopes in the positive x-dimension of our domain or east, thus $\beta = 0$.

The buoyancy term in Equation \ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density. The along-slope pressure gradient is set by the ambient density of the water column $\rho_a$. This ambient density is determined using the initial far-field ocean density. For a non-sloping domain, $\rho_a$ = $\rho_i$
% the far-field density remains constant during the simulation due to relaxation boundary conditions
% temperature and salinity values and the initial vertical hydrostatic pressure profile in the middle of the domain. 
%Thus, we assume that the evolution of density in the boundary layer does not significantly affect buoyancy/ice-shelf slope. 
We neglect hydrostatic pressure gradients along slope. For the maximum slope simulated in this study, the maximum hydrostatic pressure gradient is on the order of 1 bar m\textsuperscript{-1}. % or 10 pa/m
This simplification has the advantage of avoiding pressure discontinuities across periodic boundary conditions. 
%We assume that density differences between ambient and simulated conditions does not significantly change as a function of along-slope pressure changes. 
% \begin{equation}
%     \rho(T(x,z),S(x,z),p(x,z)) - \rho_a(T_a,S_a,p(x,z)) \approx 
%     \rho(T(x,z),S(x,z),p(x_{mid},z) - \rho_a(T_a,S_a,p(x_{mid},z))
% \end{equation}
%These density differences are verified to be within XX $kg/m^3$ for these simulations.

%\paragraph{}%Surface drag
The last term in Equation \ref{eq:uprog} represents the loss of momentum due to drag between the ice surface and the flow, where $\tau$ is the shear stress. This term is parameterized by the sub-grid scheme.

@@

\subsection{Turbulence closure}\label{meth:tcm}

The turbulence closure scheme is Anisotropic Minimum Dissipation (Rozema) employing the extension to scalars introduced by Abkar and Moin. Our implementation shows similar qualitative behavior to the stable atmospheric boundary layer published in XX; some inter-model variability is expected due to different numerics.

Momentum fluxes are parameterized according to law of the wall following a linear stability function as in Vreugdenhil and Taylor (2019):

\begin{equation}
    \vec{\tau} = \rho \overline{\vec{u}'w'} = \rho u_* \frac{ \kappa (u(z_1) - u_b}{\textrm{ln}(z_1/z_0)-\Psi_m(\zeta_1)}
\end{equation}

where $\zeta_k = z_k/L_O$, friction velocity $u_*$, $z_0$ is the roughness length, and $z_1$ is the evaluation depth at the uppermost grid cell.
\begin{equation}
    \Psi_m(\zeta) = 1 + \beta_m \zeta
\end{equation}

Similarly the sub-grid fluxes of scalars are parameterized
\begin{equation}
    \overline{w'\theta'} = \Gamma_{\theta} u_* (\theta(z_1) - \theta_b),\: 
    \overline{w'S'} = \Gamma_S u_* (S(z_1) - S_b)
\end{equation}

\begin{equation}
    \Gamma_{\theta}^{-1} = (\Gamma_{\theta,turb} + \Gamma_{\theta,mol})^{-1},\:
    \Gamma_S^{-1} = (\Gamma_{S,turb} + \Gamma_{S,mol})^{-1}
\end{equation}

\begin{equation}
    \Gamma_{\theta,turb} = \kappa^{-1} (\textrm{ln}(z_1/z_0) - \Psi_{\theta}(\zeta_1))
    % + \Psi(z_0/L_O)) % correction for roughness length
\end{equation}
\begin{equation}
    \Gamma_{S,turb} = \kappa^{-1} (\textrm{ln}(z_1/z_0) - \Psi_S(\zeta_1))
    % + \Psi(z_0/L_O)) % correction for roughness length
\end{equation}
If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($Gamma_{f}$, Table \ref{table:var}).

\begin{equation}
    \Psi_{\theta,S}(\zeta) = 1 + \beta_{\theta,S} \zeta
\end{equation}
The coefficients of these stability functions are chosen as in Wyngaard 2010; Zhou et al. 2017 (Table \ref{table:var}.

\begin{equation}
    \Gamma_{\theta,mol} = 12.5 \textrm{Pr}^{2/3} - 6
\end{equation}
\begin{equation}
    \Gamma_{S,mol} = 12.5 \textrm{Sc}^{2/3} - 6
\end{equation}
where Pr is the Prandtl number and Sc is the Schmidt number. %similarly for $\Gamma_{S,mol}$ but with Schmidt number.

We use ``virtual" freshwater fluxes as opposed to freshwater fluxes with mass or volume; thus, the scalar fluxes take the form \cite{XX}
\begin{equation}
    \overline{w'\theta'} = -c_p u_*
    (\Gamma_{\theta} - \Gamma_S \frac{S_b - S_1}{S_b})(\theta_b-\theta)
    %\rho_{sw}\overline{w'\theta'} = c_p(\rho_{sw} \Gamma_T u_* + \rho_{fw} m)(T(z_1) - T_b)
\end{equation}

\begin{equation}
    \overline{w'S'} = -u_*
    (\Gamma_S - \Gamma_S \frac{S_b - S_1}{S_b})(S_b-S)
    %\rho_{sw}\overline{w'S'} = (\rho_{sw} \Gamma_S u_* + \rho_{fw} m)(S(z_1) - S_b)
\end{equation}

%\subsection{Prognostic melt calculation}
The temperature and salinity at the ice-ocean interface, $\theta_b$ and $S_b$, are unknown. Three equations are used to solve for these quantities and the melt rate, the so-called three-equation parameterization:

\begin{equation}\label{eq:melt_1}
    \rho c_p \overline{w'\theta'}_b = -\rho_f m L_i
    %\rho c_p \overline{w'\theta'}_b - F_{T,cond} = -\rho_{fw} m L_i
\end{equation}

\begin{equation}\label{eq:melt_2}
    \rho \overline{w'S'}_b = −\rho_f m S_b
\end{equation}

\begin{equation}\label{eq:melt_3}
    \theta_b = \theta_f(p,S_b)
\end{equation}

These equations specify that heat and salt are conserved at the ice-ocean interface (Equations \ref{eq:melt_1} and \ref{eq:melt_2})and the interface temperature is fixed at the local freezing temperature using the polynomial function from \cite{jackett_2006} (Equation \ref{eq:melt_3}). Equation \ref{eq:melt_1} assumes that the conductive heat flux into ice is 0.
% short version in A01

\subsection{Simulation set-up}

The domain is a 64 m$^3$ cube with horizontal resolution of 0.5 m and vertical resolution of 0.25 m. The ice-ocean interface is located on the top boundary of the domain. Large-scale horizontal pressure gradients drive the mean flow, which is geostrophic in the far-field where buoyancy does not modify the flow. We choose a pressure of 800 dbar at the top of the domain, a rather arbitrary choice given that the depth of ice shelf bottoms ranges an order of magnitude (roughly -2000 m to -200 m). The potentially dynamically relevant differences between conducting these simulations at surface pressure and 800 dbar is that the first derivative of the freezing temperature with respect to salinity is 20\% smaller and the first derivative of density with respect to salinity is about 100\% larger.

%\paragraph{Initial and boundary conditions}
Boundary conditions for velocity, temperature and salinity are cyclic at the side boundaries, Dirichlet at the bottom boundary, and von Neumann at the top boundary. The bottom third of the domain is a sponge layer within which velocity, temperature, and salinity are relaxed toward their assigned values at the bottom of the domain. The sponge layer results in no vertical fluxes of heat, salt, or momentum across the bottom boundary. The von Neumann boundary conditions at the top of the domain correspond to the sub-grid fluxes of heat, salt and momentum (Equations XX), as resolved fluxes go to zero at a no-penetration boundary. The drag coefficient for all simulations is 0.003, a canonical value below sea ice and ice shelves though poorly constrained \cite{XX}. The drag coefficient sets the roughness length $z_0$ in the boundary flux equations of Section \ref{sec:meth_sgs} through the quadratic drag ``law of the wall." A complete list of parameter choices can be found in Table \ref{table:var}.

There are two sets of simulations which have a base case in common. The base case has low far-field thermal driving of 0.1 $^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field geostrophic flow of 20 cm s$^{-1}$ to the [XX east]. These conditions were chosen to favor a high TKE regime, for reasons discussed in Section \ref{sec:disc}. To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.1 $^{\circ}$C to 0.5 $^{\circ}$C in the first set of simulations. In the second set of simulations we reduce the slope from 1$^{\circ}$ to 0.01$^{\circ}$.

The far-field salinity for all runs is 35 g kg\textsuperscript{-1}. Initially, both temperature and salinity increase with depth over the upper two-thirds of the domain. The background salinity stratification dominates the density stratification, with an inverse stability ratio $R_\rho^*$ of 20.

The simulation duration is 50 h, corresponding to a little over 4 inertial periods. By this point, the turbulent intensity as measured by the maximum vertical velocity fluctuation, is reasonably steady-state over one inertial period for the 1$^{\circ}$-slope simulations (Figure S\ref{fig:max_w2_timeseries}).

\section{Results}

% Sensitivity to thermal driving

The fluctuations in TKE with flow orientation under inertial oscillations are replicated when the mean pressure gradient is rotated, with increased TKE when flow is oriented downslope (not shown or supplemental).

\section{Discussion}

This is the second LES study of the ice-shelf ocean boundary layer in which the boundary layer turbulence declines throughout the coarse of the simulation \cite{XX}. This results in declining melt rates as well, making it difficult to evaluate the relationship between melting and far-field conditions at steady state -- which has been central to the goal of improving ice-shelf basal melt parameterizations with the results of high-resolution simulations.
There are a few possible explanations for this phenomenon. Perhaps the best candidate is that either the sub-grid scheme or the model numerics are too dissipative, such that the TKE generated by the resolved dynamics is lost too quickly. Another possibility is that we are missing or underestimating a source of TKE in the model. Tides were not in

Furthermore, the simulations shown here have a sufficiently strong salinity gradient that the potential energy stored in the temperature gradient is not converted to TKE. Simulations now shown here suggest that simulated TKE can be maintained when stability ratios are as low as 4, but a detailed exploration of this phenomenon is not within the scope of the current work as LES cannot allow for the development of double-diffusive convection, which may occur when the stability ratio is lower than \~ 10.  
%It appears that well-mixed boundary layers are produced for a narrower range of conditions in simulations than in observations.

@@

\subsection{Tables}
\input{table1_prm-only}
